### 2018-10-11 ANA-TOPQ-2017-07-PAPER-metadata.tex
removed version number
sync local version with master

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.2}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
The high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, are exploited in the two analyses respectively. 
Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
These are the most restrictive direct bounds on $tqH$ interactions measured so far.
}

@@

% ATLAS reference code, to help ATLAS members to locate the paper
%\AtlasRefCode{TOPQ-2017-07}
\AtlasRefCode{ATLAS-CONF-2018-049}

>>>>

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.3}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
The high multiplicity of $b$-quark jets, or the presence of hadronically decaying $\tau$-leptons, are exploited in the two analyses respectively. 
Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
}

@@

% ATLAS reference code, to help ATLAS members to locate the paper
%\AtlasRefCode{TOPQ-2017-07}
%\AtlasRefCode{ATLAS-CONF-2018-049}

### 2018-10-11 sections/conclusion.tex

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$ respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.

>>>>

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming respectively $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

### 2018-10-11 sections/data_presel.tex

Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected 
with the ATLAS detector in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
Only events recorded with a single-electron trigger, a single-muon trigger, or a ditau trigger under stable beam conditions 
and for which all detector subsystems were operational are considered.
The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45 interactions, with an average of 24.
%The mean number of $pp$ interactions per bunch crossing in the dataset is 24.

@@

The above requirements apply to the physics objects as defined in Section~\ref{sec:objects}.
%, which are in general different between both searches. 
These requirements, which ensure a negligible overlap between the $\Hbb$ and $\Htautau$ searches,
are referred to as the ``preselection'' and are summarised in Table~\ref{tab:preselection}.

>>>>

Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
Only events recorded with a single-electron trigger, a single-muon trigger, or a ditau trigger under stable beam conditions 
and for which all detector subsystems were operational are considered.
The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45 interactions, with an average of 24.
%The mean number of $pp$ interactions per bunch crossing in the dataset is 24.

@@

The above requirements apply to the reconstructed objects defined in Section~\ref{sec:objects}.
%, which are in general different between both searches. 
These requirements, which ensure a negligible overlap between the $\Hbb$ and $\Htautau$ searches,
are referred to as the preselection and are summarised in Table~\ref{tab:preselection}.

### 2018-10-11 sections/introduction.tex

Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
%See Ref.~\cite{Agashe:2013hma} for a review.
%\textbf{Update a bit above paragraph mentioning more recent models.}

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. 
Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as ``multileptons",
are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton signatures resulting from 
$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
Compared to previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}.

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes.
Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production (i.e. $pp \to tH$ production is ignored), and targeting the 
$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
The latter requirement is aimed at selecting events with a hadronically-decaying $W$ boson, since this allows an improved reconstruction of the
event kinematics.

>>>>

Following the observation of the Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
%See Ref.~\cite{Agashe:2013hma} for a review.
%\textbf{Update a bit above paragraph mentioning more recent models.}

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. 
Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton signatures resulting from 
$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
Compared to previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}.

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes.
Therefore, they help to complete the programme of searches for $t \to Hq$ decays of the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production), and targeting the 
$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
The latter requirement is aimed at selecting events with a hadronically decaying $W$ boson, since this allows an improved reconstruction of the
event kinematics.
